Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-05-18 PAPER/main.tex
added bullet points to comparison
added bullets to comparison, removed comments end speed times

The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz. The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the number of strips $k$ in the optimal solution, which was calculated using Equation \ref{eqn:lowerbound}.

@@

@@

\textbf{Speed $n$ = 500}
\begin{itemize}
	\item MFFD $W = 5000$ Average speed = 38.88504ms/instance
	\item MFFD $W = 2500$ Average speed = 38.55795ms/instance
	\item MFFD $W = 1250$ Average speed = 37.98091ms/instance
	\item PS $W = 5000$ Average speed = 42.11938ms/instance
	\item PS $W = 2500$ Average speed = 44.24521ms/instance
	\item PS $W = 1250$ Average speed = 49.66614ms/instance
	\item MFFD$^+$ $W = 5000$ Average speed = 214.04479ms/instance
	\item MFFD$^+$ $W = 2500$ Average speed = 190.36579ms/instance
	\item MFFD$^+$ $W = 1250$ Average speed = 214.78729ms/instance
\end{itemize}

\textbf{Speed $n$ = 1000}
\begin{itemize}
	\item MFFD $W = 5000$ Average speed = 159.68755ms/instance
	\item MFFD $W = 2500$ Average speed = 157.92673ms/instance
	\item MFFD $W = 1250$ Average speed = 154.45345ms/instance
	\item PS $W = 5000$ Average speed = 168.77291ms/instance
	\item PS $W = 2500$ Average speed = 176.81209ms/instance
	\item PS $W = 1250$ Average speed = 201.522ms/instance
	\item MFFD$^+$ $W = 5000$ Average speed = 825.59964ms/instance
	\item MFFD$^+$ $W = 2500$ Average speed = 744.73509ms/instance
	\item MFFD$^+$ $W = 1250$ Average speed = 434.67655ms/instance
\end{itemize}
\end{comment}
\begin{comment}
\section{Further Work}
\begin{itemize}
	\item mffd+ items are packed one by one, could be a case where an items fits onto a strip but ahc cannot find a feasible solution, so item must be packed elsewhere, but if two new items could fit on the strip, ahc might be able to find a solution. 
	\item include item width in ahc, so add values to the blue edges of the graph, weighted edges, red edges have value = 0.
	\item Then the problem would be: find the minimum number of alternating cycles on $G$ such that the length of the cycle is less than or equal to some value $W$ (which is the strip width). The length of the cycle would be the sum of all the weighted edges, so the sum of all the blue edges, since red = 0. 
	\item then could break and form edges to create new components of different sizes if some are too large, or join together if some are small, thus decreasing the number of cycles
	\item or if possible, find a single alt Ham cycle, and break up into as few smaller cycles as possible such that the length of each cycle is less than or equal to $W$
	\item another way, create as few feasible subsets $\mathcal{I}' \subseteq \mathcal{I}$ such that the total width of the items in each subset $\mathcal{I}$ is less than $W$, i.e. perform usual FFD alg, ignore score widths
	\item then perform ahc on each set, try to find feasible solution.
	\item if sets dont have feasible solution, try swapping items between sets
	\item initial tests, Becker theorem 6 2015 paper 
\end{itemize}
\end{comment}

>>>>

The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz. The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the lower bound for the number of strips $k$, which was calculated using Equation \ref{eqn:lowerbound}.

@@

\begin{itemize}
	\item ``BPP becomes easier to solve when the number of items per bin increases, and problems with two or less items per bin are trivial to solve. Triplers are proposed to be `the most difficult bin packing instances''' \cite{falkenauer1996}.
	\item Fair comparison, running over 1000 instances (average of 1000 instances)
	\item Note that MFFD and MFFD$^+$ perform identically when $\delta = 1.0$, as they both perform in exactly the same manner as the original FFD heuristic  
	\item All instances completed in less than 160ms
	\item PS is not able to reach highest optimality in any case from $\delta = 0.8$ onwards.
\end{itemize}

@@

\end{comment}
\begin{comment}
\section{Further Work}
\begin{itemize}
	\item mffd+ items are packed one by one, could be a case where an items fits onto a strip but ahc cannot find a feasible solution, so item must be packed elsewhere, but if two new items could fit on the strip, ahc might be able to find a solution. 
	\item include item width in ahc, so add values to the blue edges of the graph, weighted edges, red edges have value = 0.
	\item Then the problem would be: find the minimum number of alternating cycles on $G$ such that the length of the cycle is less than or equal to some value $W$ (which is the strip width). The length of the cycle would be the sum of all the weighted edges, so the sum of all the blue edges, since red = 0. 
	\item then could break and form edges to create new components of different sizes if some are too large, or join together if some are small, thus decreasing the number of cycles
	\item or if possible, find a single alt Ham cycle, and break up into as few smaller cycles as possible such that the length of each cycle is less than or equal to $W$
	\item another way, create as few feasible subsets $\mathcal{I}' \subseteq \mathcal{I}$ such that the total width of the items in each subset $\mathcal{I}$ is less than $W$, i.e. perform usual FFD alg, ignore score widths
	\item then perform ahc on each set, try to find feasible solution.
	\item if sets dont have feasible solution, try swapping items between sets
	\item initial tests, Becker theorem 6 2015 paper 
\end{itemize}
\end{comment}
